%-------------------------
% Resume in Latex
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{csquotes}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
    \item\small{
        \textbf{#1}{: #2 \vspace{-2pt}}
    }
}

\newcommand{\resumeSubheading}[4]{
    \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1}       & #2                 \\
        \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
    \hspace{1em}%
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\techStack}[1]{\textit{Tech stack}{: #1}}


%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{{\Large Ivan Antipin}} & Email: \href{mailto:ivan.antipin@gmail.com}{ivan.antipin@gmail.com}\\
& Mobile: +(45)50173238 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Moscow Aviation Institute}{Moscow}
{Master in computer science and mathematics}{Sep. 1998 -- Feb. 2005}
\resumeSubHeadingListEnd

%-----------ABOUT-----------------
\section{Profile}
\resumeSubHeadingListStart
Technology agnostic, passionate developer and experienced technical lead with more that 15 projects completed.
I have deep understanding of software development and practical mind. Fluent at designing and implementing systems from scratch.
\resumeSubHeadingListEnd


%-----------Employment-----------------
\section{Employment}
\resumeSubHeadingListStart

\resumeSubheading
{Nordea Bank}{Copenhagen, Denmark}
{Chief IT Developer, Team Lead}{Feb 20015 - Present}

\textit{Achievements:}
\begin{itemize}
\item Designed and implemented highly available, horizontally scalable, long term storage with gRPC API.
\subitem {
\techStack { Java/Cassandra/gRPC/Kafka/Avro/Docker}
}
\item Reengineered, designed API and led main Nordea trade storage and validation system development.
\subitem {
\techStack {Java/Mongo/gRPC/Kafka/Docker}
}
\item Designed, implemented and led in-house replacement of failed 3rd party limit management system.
\subitem {
\techStack {Kotlin/Kafka/Docker/REST/OpenApi/React/TypeScript}
}
\item Designed and led implementation of alternative to multi-million 3rd party product for complex messaging processing.
\subitem{
\techStack { Kotlin/Kafka/Docker/SQLite/REST/OpenAPI/TypeScript/React}
}
\item Reimplemented and led development of API for strategic static data system.
\subitem{
\techStack { Kotlin/Kafka/Docker/CQEngine/REST/OpenAPI/TypeScript/React}
}
\item Replaced legacy major risk engine with streaming approach and speed it up more than x10 times.
\subitem{
\techStack { Java/REST/Redis/Oracle}
}
\item Worked across teams to promote best programming practices.
\item Developed interview process pipeline.
\item Influenced GRPC based API development in Nordea as alternative to REST for system-to-system communications.
\item Influenced and promoted Kotlin usage in Nordea as better alternative to Java.
\end{itemize}

\resumeSubheading
{Deutsche Bank}{Moscow, Russia}
{Senior Software Engineer (AVP)}{Apr 2012 - Nov 2014}

\textit{Achievements:}
\begin{itemize}
\item Designed and implemented backend of risk management system.
\subitem{
\techStack { Java/Oracle Coherence}
}
\end{itemize}

\resumeSubheading
{Luxoft}{Moscow, Russia}
{Senior Software Engineer}{March 2011 - March 2012}

\textit{Achievements:}
\begin{itemize}
\item Development of a low latency, price distribution system with zero GC.
\end{itemize}
\techStack{ Java/NIO/Multicast}

\resumeSubheading
{Deutsche Bank}{Moscow, Russia}
{Senior Software Engineer}{Apr 2005 - Nov 2010}

\textit{Achievements:}
\begin{itemize}
\item Designed and implemented main order management system with embedded matching engine. Reduced latency and throughput x5 comparing to previous system.
\item Implemented declarative BDD framework ( a-la Cucumber style that was non-existent that time).
\item Reimplemented price distribution engine of AutobahnFX.
\end{itemize}

\techStack{ Java/JMS/Sockets/Oracle}

\resumeSubHeadingListEnd

\section{Side activities}

\begin{itemize}
\item Strategy back-tester for algo trading in kotlin, typescript.
\item Telegram bot for technical analyses \href{https://web.telegram.org/z/#1072760314}{https://web.telegram.org/z/#1072760314} .
\item AI research with python, pandas, numpy, scikit-learn libs.
\end{itemize}

%
%--------SKILLS------------
\section{Skills}
\begin{itemize}
\item \textbf{Languages}{: Kotlin/Java/C-sharp/Typescript/Python/SQL}
\item \textbf{Technologies}{: Kafka/Docker/Mongo/gRPC/React/Avro/Protobuf/Cassandra}
\item \textbf{Other}{: Algorithms/Computer Science/Machine Learning/Gradle/Bash/Unix/Git}
\end{itemize}

\section{Recommendations}



\renewcommand{\mkbegdispquote}[2]{\itshape}

\textbf{Tam Freestone Bayes}

Startup/Fintech CEO/CTO/CIO

Banking IT architecture, engineering and execution leadership; Oxon & Cantab

\begin{displayquote}
Incisive and highly autonomous, Ivan is one of the most potent developers I know.
He swiftly gets to the core of a problem, makes sensible, pragmatic technical choices, then produces - and as requirements evolve, rapidly iterates upon - clean, succinct solutions. While he has no difficulty in adopting new technologies when they are the right tool for the job, he defaults to simplicity in his designs. If something needs to be done well, and quickly, then ask Ivan to do it.
\end{displayquote}

\textbf{Arasa Velaigam}

Head of Subsidiary Accounting at Nordea
\begin{displayquote}
Ivan is an excellent developer and driver of technical solutions to very complex problems. His communication is efficient and he is able to quickly identify challenges, evaluate alternatives and solutions in an open discussion across varying user groups.
I have witnessed Ivan continually develop his technical skills increasing his delivery capabilities and skillset.
He is pragmatic and result orientated thus easily able to balance delivery timelines with changing requirements, priorities and infrastructure dependency issues outside his scope.
\end{displayquote}

\textbf{Anton Polyakov}

Senior Engineering Manager at Google

\begin{displayquote}
I worked with Ivan and was his direct manager for a couple of years in Nordea Denmark. Ivan is a "10x developer". When I landed at Nordea I realized I needed a "break through" swat team to really move the needle and modernize core of our systems as well as seed the right engineering culture. Ivan was the core and founding member of such team. Capable, fast learning, bright and dedicated effective both at dealing with legacy systems as well as working on a cutting edge projects, with his help we went from an old PL/SQL core to an in-memory compute engine and from an old Oracle based warehouse with rigid and hard to evolve structure to a flexible document-based horizontally scalable data service with streaming API on top. Ivan sets and maintains a very high engineering standards bar but was capable of doing a well calculated compromises not imp[acting fundamental quality when we really needed to ship.
Don't be misled by Ivan's direct communication style, it comes handy when you will need to get lots of work done and in no way it hinders Ivan's team player capabilities (he is a good team player and a capable tech lead)
\end{displayquote}


\section{My development practices}


\begin{itemize}
\item Complexity and technical debt management is in the top of my objectives while designing and implementing project. Improper management often leads to a exponential complexity growth to the system functionality.
\item While leading a team I try to avoid redundant people sidetracking and context switching to micro tasks as this is very expensive.
\item Cross team communication can be greatly improved by extensive usage of systems contracts/APIs, as people are "slow" computers are "fast".
\item I prefer functional approach over OOP which is often overused.
\end{itemize}

%-------------------------------------------
\end{document}
